Painting with Triangles

### 2014-06-06 paper.tex
Reduced the spacing
tweaks to marks' modifications.

% uncomment one the following two lines, first one showing pictures
\documentclass[annual]{acmsiggraph}
%\documentclass[annual,draft]{acmsiggraph}

@@

A set of contours define the outline of a stroke. For simply connected strokes, those without holes, 
one contour describes the whole stroke. However, strokes with holes, such as a circle or 
figure-eight, will have more than one contour.
Converting a user's mouse motion into a set of contours requires two steps.
First, the user's mouse movements are captured by a set of polygons which can be
rendered to yield a rasterized version of the stroke. \modified{This rasterization happens at the resolution of the current window. Therefore
whatever the artist sees on the screen is the basis for the vectorization.}
Second, to obtain the contours the stroke is rasterized in black and marching squares~\cite{lorensen1987}
is used to extract iso-contours of 50\% gray. This returns a very dense set of points,
which we reduce through a pruning process to
get a sparse but accurate representation of the contour.
The pruning procedure walks around the contour to form an approximating polygon $P$,
greedily eliding vertices whenever they lie within a small threshold distance of $P$. \modified{We use
a threshold relative to zoom of 0.5 which was determined to work well empirically.}

@@

\section{Results and Discussion}
Paintings made with our system in a range of visual styles are shown in Figures~\ref{fig:teaser} and \ref{fig:face}--\ref{fig:stop}.  
%
The images shown in \fig{fig:boxes}
reveal a drawing with an extreme zoom range up to 524,000:1, 
for an effective resolution equivalent to an image with more than $10^{17}$ pixels.
At this zoom level our renderer begins to suffer from artifacts at 
the limits of single floating point precision; 
this could be ameliorated by switching to double-precision. \modified{Traditional vector
graphics software such as Adobe Illustrator caps zooming at a ratio of 64:1. Although this
is not an inherent limitation, there is currently not a way to use such vector graphics programs
to draw using a traditional painting metaphor with gradients while so zoomed in.}

@@

Figure~\ref{fig:timing} gives a similar result for the cumulative time strokes take to render. Both
the zooming and non-zooming cases grow non-linearly over time. However, the non-zooming case takes
longer for the reasons described. \modified{For example, the first ten strokes in both cases take about 2 seconds
to render. While the last ten strokes take about 20 seconds in the non-zooming case and 7 seconds in the zooming case.}
It is not unexpected that even the zooming case grows non-linearly
since even though the geometries involved are not becoming very complicated, the geometry of the entire
canvas is increasing linearly and must be considered even if the entire canvas is not re-triangulated.

\modified{Note that all these numbers come from running the program on a 1.8 GHz Core i5 MacBook Air with 8GB of RAM and an Intel HD 4000 graphics card.}

@@

\modified{Beyond reducing the complexity of the geometry, the speed of the algorithm might be improved by
utilizing the GPU. For example, Nehab and Hoppe~\shortcite{Nehab:2008:RRG:1409060.1409088} demonstrate an
approach for using GPUs to speed up rending of more traditional vector graphics.}

@@

\subsection{Performance}
The current implementation uses Python and PyOpenGL. Python's performance is slower than
a lower level implementation in C++ would be. The preview rasterization of a new stroke on 
the canvas is interactive with
no lag. However, the actual process to take a stroke from rasterization to triangle
representation on the canvas can be slow. On a blank canvas, strokes take less than
one second to process. However, on a canvas with lots of geometry a stroke that overlaps
that geometry can take several seconds to render. Some of this could be alleviated by a carefully optimized implementation. However, there are many calculations
necessary for the old points affected by the new stroke and the points associated with the
new stroke itself. Since these geometries can become arbitrarily complicated (in pathological cases), these
calculations can take arbitrarily long.
% This brings us to the final point, simplification.

@@

\modified{
\section*{Acknowledgments}
Let's add something here.
}

>>>>

% uncomment one the following two lines, first one showing pictures
\documentclass[conference]{acmsiggraph}
%\documentclass[annual,draft]{acmsiggraph}

@@

A set of contours define the outline of a stroke. For simply connected strokes, those without holes, 
one contour describes the whole stroke. However, strokes with holes, such as a circle or 
figure-eight, will have more than one contour.
Converting a user's mouse motion into a set of contours requires two steps.
First, the user's mouse movements are captured by a set of polygons which can be
rendered to yield a rasterized version of the stroke. \modified{This rasterization happens at the resolution of the current window. Therefore
whatever the artist sees on the screen is the basis for the vectorization.}
Second, to obtain the contours the stroke is rasterized in black and marching squares~\cite{lorensen1987}
is used to extract iso-contours of 50\% gray. This returns a very dense set of points,
which we reduce through a pruning process to
get a sparse but accurate representation of the contour.
The pruning procedure walks around the contour to form an approximating polygon $P$,
greedily eliding vertices whenever they lie within a small threshold distance of $P$. \modified{We use
a threshold of 0.5 pixels at the current zoom level, which works well empirically.}

@@

\section{Results and Discussion}
Paintings made with our system in a range of visual styles are shown in Figures~\ref{fig:teaser} and \ref{fig:face}--\ref{fig:stop}.  
%
The images shown in \fig{fig:boxes}
reveal a drawing with an extreme zoom range up to 524,000:1, 
for an effective resolution equivalent to an image with more than $10^{17}$ pixels.
At this zoom level our renderer begins to suffer from artifacts at 
the limits of single floating point precision; 
this could be ameliorated by switching to double-precision. \modified{This significantly exceeds the limits
imposed by existing vector graphics software such as Adobe Illustrator, which has a maximum zoom ratio
of 64:1.  Furthermore, our ability to make paint strokes of smooth gradients in a flat vector representation (see Figure~\ref{fig:teaser}) is unique.}

@@

Figure~\ref{fig:timing} gives a similar result for the cumulative time strokes take to render. Both
the zooming and non-zooming cases grow non-linearly over time. However, the non-zooming case takes
longer for the reasons described. \modified{For example, the first ten strokes in both cases take about 2 seconds
to render, while the last ten strokes take about 20 seconds in the non-zooming case and 7 seconds in the zooming case.}
It is not unexpected that even the zooming case grows non-linearly
since even though the geometries involved are not becoming very complicated, the geometry of the entire
canvas is increasing linearly and must be considered even if the entire canvas is not re-triangulated.

@@

\modified{Beyond reducing the complexity of the geometry, the speed of the algorithm might be improved by
utilizing the GPU more heavily. For example, Nehab and Hoppe~\shortcite{Nehab:2008:RRG:1409060.1409088}
demonstrate an approach for using GPUs to speed up rending of more traditional vector graphics.}

@@

\subsection{Performance}
Performance is measured on a 1.8 GHz Core i5 MacBook Air with 8GB of RAM and an Intel
HD 4000 graphics card.  The current implementation uses Python and PyOpenGL. Python's performance is slower than
a lower level implementation in C++ would be. The preview rasterization of a new stroke on 
the canvas is interactive with
no lag. However, the actual process to take a stroke from rasterization to triangle
representation on the canvas can be slow. On a blank canvas, strokes take less than
one second to process. However, on a canvas with lots of geometry a stroke that overlaps
that geometry can take several seconds to render. Some of this could be alleviated by a carefully optimized implementation. However, there are many calculations
necessary for the old points affected by the new stroke and the points associated with the
new stroke itself. Since these geometries can become arbitrarily complicated (in pathological cases), these
calculations can take arbitrarily long.
% This brings us to the final point, simplification.

@@

%\modified{
%\section*{Acknowledgments}
%Let's add something here.
%}
